\documentclass[11pt, letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage{geometry}
\geometry{left=0.7in, top=0.6in, right=0.7in, bottom=0.6in}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

% Colors
\definecolor{primary}{RGB}{0, 0, 0}
\definecolor{secondary}{RGB}{85, 85, 85}

% Formatting
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\titleformat{\section}{\Large\bfseries\color{primary}}{}{0em}{}[\vspace{-0.5em}\rule{\textwidth}{0.4pt}]
\titlespacing*{\section}{0pt}{2ex}{1ex}

\begin{document}
% Header
\begin{center}
    {\huge\bfseries\color{primary} Chitrada Sravani} \\ \vspace{0.3em}
    \ifx\relaxJava Full Stack Developer\relax\else
    {\large\color{secondary} Java Full Stack Developer} \\ \vspace{0.3em}
    \fi
    {\small\color{secondary}
    \ifx\relaxsravani.chitrada@example.com\relax\else\href{mailto:sravani.chitrada@example.com}{sravani.chitrada@example.com}\fi
    \ifx\relax+91 98765 43210\relax\else\ |\ +91 98765 43210\fi
    \ifx\relaxHyderabad, India\relax\else\ |\ Hyderabad, India\fi
    \ifx\relaxhttps://linkedin.com/in/sravani-chitrada\relax\else\ |\ \href{https://linkedin.com/in/sravani-chitrada}{LinkedIn}\fi
    \ifx\relax\relax\else\ |\ \href{}{Portfolio}\fi
    }
\end{center}

% Summary
\ifx\relaxMotivated Java Full Stack Developer with hands-on internship experience in building robust web applications using Java, Spring Boot, and React. Adept at designing RESTful APIs and collaborating within agile teams to deliver scalable software solutions.\relax\else
\section*{Career Objective}
Motivated Java Full Stack Developer with hands-on internship experience in building robust web applications using Java, Spring Boot, and React. Adept at designing RESTful APIs and collaborating within agile teams to deliver scalable software solutions.
\fi

% Education (First for freshers)
\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill \textit{2020 – 2024} \\
\textit{JNTU Hyderabad}
\vspace{0.5em}

% Skills
\section*{Technical Skills}
\begin{multicols}{3}
\begin{itemize}[label=•, leftmargin=*, noitemsep]
    \item {'category': None, 'skills': ['Java', 'Python', 'SQL', 'JavaScript', 'HTML/CSS', 'Spring Boot', 'React', 'Node.js', 'Hibernate', 'Git', 'Docker', 'Maven', 'PostgreSQL', 'AWS']}
\end{itemize}
\end{multicols}
\vspace{-1.5em} 

% Projects (Prominent for freshers)
\section*{Projects \& Academic Work}
\textbf{Online Food Ordering System} \\
Full-stack food ordering app with Spring Boot backend and React frontend. Integrated Stripe payments and real-time order tracking via WebSockets.
\vspace{0.5em}
\textbf{Employee Management Portal} \\
CRUD-based portal with role-based access control using Spring Security. Deployed on AWS EC2 with CI/CD via GitHub Actions.
\vspace{0.5em}

% Experience
\section*{Work Experience \& Internships}
\textbf{Java Full Stack Intern} \hfill \textit{Jun 2024 – Dec 2024} \\
\textit{\color{secondary}Skilldzire}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built RESTful APIs with Spring Boot, reducing backend response latency by 30\%.
    \item Developed React-based dashboards consumed by 500+ daily active users.
    \item Integrated PostgreSQL with Hibernate ORM, improving query efficiency by 25\%.
    \item Collaborated with a 4-person agile team, delivering 3 sprint features ahead of schedule.
\end{itemize}
\vspace{0.5em}
\textbf{Java Full Stack Intern} \hfill \textit{Jan 2024 – May 2024} \\
\textit{\color{secondary}Brain O Vision Pvt Ltd}
\vspace{-0.5em}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed user authentication module using JWT and Spring Security.
    \item Created reusable React components that cut front-end development time by 40\%.
    \item Wrote 50+ unit tests using JUnit and Mockito, achieving 85\% code coverage.
\end{itemize}
\vspace{0.5em}

\end{document}